---
title: "Rworkshop"
subtitle: "Practice part"
author: "Bolin Wu"
institute: "Aging Research Center"
date: '2022-03-24 (updated: `r Sys.Date()`)'
output: 
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: arta
      highlightLines: true
      contIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(htmltools.dir.version = FALSE,
        htmltools.preserve.raw = FALSE)
```




# Test 

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.



## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3


---

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars) 
```

---

## Slide with Plot

```{r pressure,  fig.height=4, dev='svg'}
plot(pressure)
```

